### 2024-01-14 inst/scripts/papertest.Rmd
exploraion script

initcomus=initialiseCommunities(traits=traits,coordinates=coordinates,G=G,sizes=100,plot=T)

@@

```{r runburnin,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=500
tpcomu=initcomus
tpcomu$occupation[,]=1
burnin=modelVector(
   K=ki, m=1, b=0.2, r=0, rho=0, d=0.01, maturity=18, endrepro=65, 
   population=population, 
   comus=tpcomu, 
   tstep=tstep, 
   tp=initNeutralTraitsPathways(z = z) , #we recreate a temporary neutral trait table with no neutral transmission
   age.threshold=20, 
   out=c("finalpop","finalcomus"),   #we only want the final population
   beta=-1,
   logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 50
)
population=resetIds(burnin$population)
initcomus$size=burnin$finalcomus$size
```

@@

```{r,eval=F}
tstep=20000
repli=50
neutraltraitsParam$s=c(.5,.5,.5,.5)
rhodep=lapply(c(0,1),function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           allinlaw=replicate(repli,
                              {
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)

           neutraltraitsParam$post[,"i"]=0
           neutraltraitsParam$post[,"h"]=1
           allposthoriz=replicate(repli,{
                                  set.seed(as.numeric(Sys.time())+r)
                                      quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                      pop=quickV$population
                                      sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)

           neutraltraitsParam$post[,"h"]=0
           neutraltraitsParam$pre[,"h"]=1
           allprehoriz=replicate(repli,{
                                  set.seed(as.numeric(Sys.time())+r)
                                     quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                     pop=quickV$population
                                     sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)

```{r,out.width="30%"}
rhodep=readRDS("precomp.RDS")

>>>>

initcomus=initialiseCommunities(traits=traits,coordinates=coordinates,G=G,sizes=50,plot=T)

@@

```{r runburnin,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=500
tpcomu=initcomus
tpcomu$occupation[,]=1
burnin=modelVector(
   K=ki, m=1, b=0.2, r=0, rho=0, d=0.01, maturity=18, endrepro=65, 
   population=population, 
   comus=tpcomu, 
   tstep=tstep, 
   tp=initNeutralTraitsPathways(z = z) , #we recreate a temporary neutral trait table with no neutral transmission
   age.threshold=20, 
   out=c("finalpop","finalcomus"),   #we only want the final population
   beta=-1,
   logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 50
)
population=resetIds(burnin$population)
initcomus$size=burnin$finalcomus$size
traitsid=paste0("t",1:z)
```

@@

```{r,eval=F}
library(parallel)
tstep=20000
repli=20
cl <- makeCluster(20,type="FORK",outfile="log.txt")
rhodep=lapply(c(.5,1),function(rho){
                  parSapply(cl,1:repli,function(i)
                                     {
                                         set.seed(as.numeric(Sys.time())+i)
                                         modelVector(
                                                          K=ki+km, m=1, b=0.2, r=0.01, rho=rho, d=0.01, 
                                                          maturity=18, endrepro=65, 
                                                          population=population, 
                                                          comus=initcomus, 
                                                          tstep=tstep, 
                                                          tp=neutraltraitsParam,
                                                          age.threshold=20, 
                                                          out=c("finalpop","finalcomus","traitsumary","popsize"), #this time we keep track of more things
                                                          logging=c("done"),
                                                          beta=-1,
                                                          ma=1,traitsid=paste0("t",1:z),F_Th = 100
                                         )
                                     })

})
stopCluster(cl)
saveRDS(file="test.RDS",rhodep)
```

```{r,out.width="30%"}
saveRDS(file="testShort.RDS",rhodep)
